### 2019-08-08 reports/thesis/chapters/5_inference.tex
inference chapter
subroi for more projections
use of dotsc
plot sub roi section

Disagreement between the scan and \texttt{aRTist} can be found by subtracting one image from the other, any values too big in magnitude can be considered as a defect. However in the previous chapters, it was found that x-ray photons behave randomly and differences in the comparison can be due to chance. Thus the comparisons should be done under the face of uncertainty.

A pixel by pixel inference was proposed to do defect detection. A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{scan}_{x,y} - \texttt{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{scan}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the scan. Under mild assumptions, it was shown in the previous chapters that the grey values in the scan were Normal. Thus by treating the simulated image from \texttt{aRTist} as known and the ground truth, then the randomness of the test statistics, assuming there are no defects, can be approximately quantified as
\begin{equation}
Z_{x,y}\sim \normal(0,1) \ .
\end{equation}
As with usual statistical convention, upper case $Z$ denote a random variable. Lower case $z$ denote a realisation or an observation of that random variable.

The variance model, $\widehat{\variance}\left[\text{scan}_{x,y}\right]$, can be calibrated, or trained, by holding out a number replicated x-ray images of a 3D printed sample. These replicated x-ray images were manually segmented. This provided variance-mean data and was used to train the variance model, such as a gamma distributed GLM. The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model. The variance was then predicted using the grey value in the \texttt{aRTist} simulation as the predictor variable.

The 20 x-ray images were spilt into 2. 19 images were used to train the variance-mean model. One image, called the test image, was used to compare with \texttt{aRTist}. In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there. The test image and the \texttt{aRTist} simulation is shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist} respectively.

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_scan.eps}
      \caption{X-ray image}
      \label{fig:inference_inferenceIntro_inference_scan}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_artist.eps}
      \caption{\texttt{aRTist} simulation}
      \label{fig:inference_inferenceIntro_inference_artist}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_logp.eps}
      \caption{$-\log p\text{-values}$}
      \label{fig:inference_inferenceIntro_inference_pvalue}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_positivePixels.eps}
      \caption{Positive pixels}
      \label{fig:inference_inferenceIntro_inference_positivePixels}
    \end{subfigure}
  }
  \caption{An x-ray image of a 3D printed cuboid, from the \texttt{Sep16 120deg} dataset, was compared to the \texttt{aRTist} simulation to detect the purposefully manufactured voids. The $p$-values obtained were used for hypothesis testing, using the \cite{benjamini1995controlling} procedure, at the 5\% FDR level. Pixels detected as positive are shown in red in d).}
  \label{fig:inference_inferenceIntro_inference}
\end{figure}

For each pixel, a test statistic was calculated. A test statistic too large in magnitude will classify that pixel as a positive result. In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be used to represent test statistic in a different way
\begin{equation}
  p_{x,y} = 2(1-\Phi(|z_{x,y}|))
\end{equation}
which can takes values $0\leqslant p_{x,y} \leqslant 1$. A $p$-value too small is considered a positive result. The $p$-values are shown in Figure \ref{fig:inference_inferenceIntro_inference_pvalue}.

@@

Model misspecification appeared to be the main source of error. The test statistics and $p$-values were inspected in Figure \ref{fig:inference_inferenceIntro_histogram}. It can be seen that the majority of the test statistics does not look Normal. Also the majority of the $p$-values does not look uniformly distributed. This seems to suggest that the assumption of $Z_{x,y}\sim \normal(0,1)$ is incorrect.

\begin{figure}[htp]
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_histogram.eps}
    \caption{Histogram}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_pValue.eps}
    \caption{$p$-values}
    \label{fig:inference_inferenceIntro_pvalue}
  \end{subfigure}
}
  \caption{a) The histogram of the test statistics is compared with the standard Normal distribution. The standard Normal distribution is known as the null distribution in this scenario. b) The $p$-values are ordered and plotted. The critical region corresponds to controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} procedure. The dotted line shows the result if the $p$-values were uniformly distributed.}
  \label{fig:inference_inferenceIntro_histogram}
\end{figure}

@@

In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user defined significance level $\alpha$, also known as the size of the test in this specific example. A positive result is declared when $p<\alpha$, else it is a negative result. Correct and incorrect testing of the statistics can occur. For example testing a null statistic as positive is known as a false positive. It can be shown that $\alpha$ controls the false positive rate. $\alpha=5.0\%$ is a typical choice and was used throughout this thesis. Other fields use the $\sigma$ notation, for example $2\sigma$ correspond to about the $\alpha = 4.6\%$ significance level; this notation will not be used here.

Multiple hypothesis testing occurs when there are more than one hypotheses to test. For example $n$ pixels can be tested where the test statistics are $Z_1, Z_2, \cdots, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\cdots,n$. The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\cdots,n$. Let the corresponding $p$-values be $p_1, p_2, \cdots, p_n$.

@@

\begin{table}[htp]
  \centering
  \begin{tabular}{c|c|c|c}
    &Negative&Positive&Total\\\hline
    Null & $U$ & $V$ & $n_0$\\
    Non-null & $T$ & $S$ & $n-n_0$\\\hline
    &$n-R$&$R$&$n$
  \end{tabular}
  \caption{Random variable definitions for the number of true/false positives/negatives made in multiple hypothesis testing}
  \label{table:inference_randomvariables}
\end{table}

The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the family-wise error rate (FWER) \citep{shaffer1995multiple} where
\begin{equation}
  \text{FWER} = \prob(V\geqslant1) \ .
  \label{eq:inference_fwer}
\end{equation}
This is done by adjusting the size of the test to be $\alpha/n$. By using the adjusted size, then $\text{FWER}=1-\left[(1-\alpha/n)^n\right]$. Using the approximation $(1-\alpha/n)^n\approx 1-\alpha$ then $\text{FWER}\approx \alpha$. This shows that the Bonferroni correction controls the family-wise error rate such that
\begin{equation}
  \text{FWER} \leqslant \alpha \ .
\end{equation}
However in practice the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it does give too many false negatives. This is because the correction traded too many false positives for false negatives.

@@

The BH procedure adjust the size of the test between the Bonferroni correction and the uncorrected test. It adapts to the data and choose different sizes for different data. The procedure is as follows, the $p$-values are ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(n)}$. Suppose a size $\alpha$ is provided beforehand. The size is then adjusted to
\begin{equation}
  \alpha_{\text{BH}} = \frac{\alpha k}{n}
\end{equation}
where
\begin{equation}
  k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{n}\alpha
  \ .
\end{equation}
This test the statistics with $p$-values $p_{(1)},p_{(2)},\cdots,p_{(k)}$ as positive. For the case where $p_{(1)}>\alpha/n$ then $k=1$ so that the Bonferroni correction is used when there are no positive results, this is only for illustration purposes. For example in Figure \ref{fig:inference_inferenceIntro_pvalue}, the $p$-values were plotted against their order so that the critical boundary was shown by a linear curve with gradient $\alpha/n$.

@@

\begin{table}[htp]
    \centering
    \begin{tabular}{c|c}
        Correction&Controls for\\\hline
        No correction&$\text{PCER}\leqslant\alpha$\\
        Bonferroni&$\text{FWER}\leqslant\alpha$\\
        BH&$\text{FDR}\leqslant\alpha$
    \end{tabular}
    \caption{Different types of corrections for multiple hypothesis testing are listed here, along with what they control for.}
    \label{table:inference_corrections}
\end{table}

Consider a small example where a $200\times200$ section of the $z$ image was investigated, as shown Figure \ref{fig:inference_inferenceSubsample1_histogram}. The distribution of the test statistics looked Normal but not centred at zero, as a result using the BH procedure obtained a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$. Almost half of the pixels were tested positive. It is questionable whether such a number of positive results is sensible, in particular in an area where defects were not expected.

\begin{figure}[htp]
  \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_zImage.eps}
      \caption{Test statistics}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_histogram.eps}
      \caption{Histogram of test in sub-image}
    \end{subfigure}
    }
    \caption{The resulting $z$ image is shown in a). A $200\times 200$ sub-image was taken shown by the dashed lines. A histogram of the test statistics in the sub-image is shown in b). The critical region was obtained by using the BH procedure at the 5\% FDR level.}
    \label{fig:inference_inferenceSubsample1_histogram}
\end{figure}

@@

In practice $\mu_0$ and $\sigma_0$ are unknown. The empirical null \citep{efron2004large} replaces the parameters of the null distribution with its estimate. Suppose $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ are the estimated null mean and null standard deviation respectively. The statistics are specified by $Z_i\sim\normal(\mu_i, \widehat{\sigma}_0^2)$ so that the following null hypotheses $H_{0,i}:\mu_i=\widehat{\mu}_0$ are tested against $H_{1,i}:\mu_i\neq\widehat{\mu}_0$ for $i=1,2,\cdots,n$.

@@

The null standard deviation is estimated from the log density \citep{efron2004large}. For values of $z$ at and around the mode
\begin{equation}
  \ln p_{Z}(z) = 
  \ln\left[
    \dfrac{\pi_0}{\sqrt{2\pi}{\sigma}_0}
  \right]
  -\dfrac{1}{2}
  \left(
    \dfrac{z-{\mu}_0}{{\sigma}_0}
  \right)^2
  \ .
\end{equation}
Taking derivatives
\begin{equation}
  \dfrac{\partial}{\partial z} \ln p_{Z}(z) =
  -\left(
    \dfrac{
      z-{\mu}_0
    }
    {
      {\sigma}_0^2
    }
  \right)
\end{equation}
\begin{equation}
  \dfrac{\partial^2}{\partial z^2} \ln p_{Z}(z) =
  -\dfrac{
    1
  }
  {
    {\sigma}_0^2
  }
\end{equation}
which motivates the estimator \citep{efron2004large}
\begin{equation}
  \widehat{\sigma}_0 = \left[
    \left.
      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}(z)
    \right|_{z=\widehat{\mu}_0}
  \right]^{-1/2}
  \ .
\end{equation}
The evaluation of $z=\widehat{\mu}_0$ is used because at the mode, it was assumed that the null test statistics would dominate and non-null test statistics would not contribute much to the density estimate.

@@

The empirical null is used widely, including in neuroimaging \citep{schwartzman2008false, schwartzman2009empirical} and has been extended to include non-Normal null distributions \citep{schwartzman2008false, schwartzman2008empirical}. There exist various methods for the empicial null. \cite{schwartzman2008empirical} uses Poisson regression on the histogram counts in regions where the null statistics dominate. The empirical characteristic function was used in \cite{jin2007estimating}.

@@

Return back to the sub-image example in Figure \ref{fig:inference_inferenceSubsample1_histogram}. The histogram was smoothed using a kernel density estimate \citep{parzen1962on, friedman2001elements} as shown in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}. The kernel density estimate \citep{parzen1962on} is
\begin{equation}
  \widehat{p}_Z(z)=
  \frac{1}{nh}
  \sum_{i=1}^n\phi\left(
    \dfrac{z_i-z}{h}
  \right)
  \label{eq:inference_kernel_density_estimate}
\end{equation}
where $h$ is the bandwidth. The bandwidth was chosen such that
\begin{equation}
  h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_z,\text{IQR}_z/1.34\right)
  \label{eq:inference_ourruleofthumb}
\end{equation}
where $s_z$ and $\text{IQR}_z$ are the sample standard deviation and sample interquartile range.

\begin{figure}[htp]
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/inference/inferenceSubsample1_densityEstimate.eps}
  \caption{The density of the test statistics was estimated using a kernel density estimate. The dot dash lines show the empirical null distribution multiplied by some constant, this is to illustrate that the two densities have the same curvature at the mode.}
  \label{fig:inference_inferenceSubsample1_densityEstimate}
\end{figure}

The null parameters were estimated. The null mean was estimated by numerically finding the mode of the density estimate. The null standard deviation was estimated using the curvature of the density estimate at the mode. This resulted in the empirical null density to have the same curvature as the density estimate at the mode, this is illustrated in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}. In this particular example, it was found that $\widehat{\mu}_0=\input{../figures/inference/inferenceSubsample1_nullMean.txt}$ and $\widehat{\sigma}_0=\input{../figures/inference/inferenceSubsample1_nullStd.txt}$ to 2 decimal places.

@@

The test statistics were normalised to $T_1,T_2,\cdots,T_n$ by using
\begin{equation}
  T_i = \dfrac{
    Z_i - \widehat{\mu}_0
  }
  {
    \widehat{\sigma}_0
  }
  \label{eq:inference_empiricalNullNormalise}
\end{equation}
for $i=1,2,\cdots,n$. The normalised $p$-values were obtained by using
\begin{equation}
  p_i = 2(1-\Phi(|t_i|))
\end{equation}
and then were used in the BH procedure. The critical region was found to be $|t|\geqslant\inputNumber{../figures/inference/inferenceSubsample1_nullNormalisedCritical.txt}$. In terms of the original units, the critical region was $z \leqslant \inputNumber{../figures/inference/inferenceSubsample1_nullCritical1.txt}$ and $\inputNumber{../figures/inference/inferenceSubsample1_nullCritical2.txt}\leqslant z$, all to 2 decimal places. The critical region and the normalised $p$-values are shown in Figure \ref{fig:inference_inferenceSubsample1_nullResults}.

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_nullHistogram.eps}
        \caption{Histogram of $z$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_nullPValues.eps}
        \caption{$p$ values}
    \end{subfigure}
    }
    \caption{The critical regions and $p$-values were adjusted using the empirical null in the sub-image example.}
    \label{fig:inference_inferenceSubsample1_nullResults}
\end{figure}

No positive results were found and the $p$-values were sensible as they looked uniformly distributed. This demonstrated that the empirical null adjusted the parameters of the null distribution to fit the majority of the data in order to make sensible inference.

>>>>

Disagreement between the obtained and the \emph{aRTist} simulated projections can be found by subtracting one projection from the other, any values too big in magnitude can be considered as a defect. However in the previous chapters, it was found that x-ray photons behave randomly and differences in the comparison can be due to chance. Thus the comparisons should be done under the face of uncertainty.

A pixel by pixel inference was proposed to do defect detection. A test statistic $Z_{x,y}$ was calculated for all pixels at $(x,y)$. This test statistic is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection. For high photon rate, it was shown in the previous chapters that the grey values in the scan can be modelled using a Normal distribution. Thus by treating the simulated projection from \emph{aRTist} as known and the ground truth, then the randomness of the test statistics, assuming there are no defects, can be approximately quantified as
\begin{equation}
Z_{x,y}\sim \normal(0,1) \ .
\end{equation}
As with usual statistical convention, upper case $Z$ denote a random variable. Lower case $z$ denote a realisation or an observation of that random variable.

To illustrate this method of inference, the projections from the dataset \texttt{AbsFilter} at \ang{120} was used. To recap, replicate projections of a test sample with purposefully manufactured voids were obtained. \emph{aRTist} was used to create a simulation of that projection but as if the voids were not there. Thus the method should pick these voids up.

A projection and the \emph{aRTist} projection is shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist} respectively. The 20 replicate projections were spilt into two. 19 randomly selected projections were used for the variance-mean model to fit onto. A gamma GLM with a basic linear relationship was used. The remaining projection was compared with the \emph{aRTist} projection, the variance was predicted using the grey value in the \emph{aRTist} simulation as the predictor variable.

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_scan.eps}
      \caption{X-ray image}
      \label{fig:inference_inferenceIntro_inference_scan}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_artist.eps}
      \caption{\texttt{aRTist} simulation}
      \label{fig:inference_inferenceIntro_inference_artist}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_logp.eps}
      \caption{$-\log p\text{-values}$}
      \label{fig:inference_inferenceIntro_inference_pvalue}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_positivePixels.eps}
      \caption{Positive pixels}
      \label{fig:inference_inferenceIntro_inference_positivePixels}
    \end{subfigure}
  }
  \caption{A projection of the test sample, from the \texttt{AbsFilter} at \ang{120} dataset, was compared to the \emph{aRTist} simulated projection to detect the purposefully manufactured voids. The $p$-values obtained were used for hypothesis testing, using the \cite{benjamini1995controlling} procedure, at the 5\% FDR level. Pixels detected as positive are shown in red in d).}
  \label{fig:inference_inferenceIntro_inference}
\end{figure}

For each pixel, a test statistic was calculated. A test statistic too large in magnitude, relative to the anticipated variance, will classify that pixel as a positive result. In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be used to represent test statistic in a different way
\begin{equation}
  p_{x,y} = 2(1-\Phi(|z_{x,y}|))
\end{equation}
which can takes values $0\leqslant p_{x,y} \leqslant 1$. A $p$-value too small is considered a positive result. The $p$-values are shown in Figure \ref{fig:inference_inferenceIntro_inference_pvalue}.

@@

Model misspecification appeared to be the main source of error. The test statistics and $p$-values were inspected in Figure \ref{fig:inference_inferenceIntro_histogram}. It can be seen that the majority of the test statistics does come from a Normal distribution. Also, the majority of the $p$-values are not look uniformly distributed. This seems to suggest that the assumption of $Z_{x,y}\sim \normal(0,1)$ is incorrect.

\begin{figure}
  \centering
  \centerline{
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_histogram.eps}
    \caption{Histogram}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_pValue.eps}
    \caption{$p$-values}
    \label{fig:inference_inferenceIntro_pvalue}
  \end{subfigure}
}
  \caption{a) The histogram of the test statistics is compared with the standard Normal distribution. The standard Normal distribution is known as the null distribution in this scenario. b) The $p$-values are ordered and plotted. The critical region corresponds to controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} procedure. The dotted line shows the result if the $p$-values were uniformly distributed.}
  \label{fig:inference_inferenceIntro_histogram}
\end{figure}

@@

In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user defined significance level $\alpha$, also known as the size of the test in this specific example. A positive result is declared when $p<\alpha$, else it is a negative result. Correct and incorrect testing of the statistics can occur. For example testing a null statistic as positive is known as a false positive. It can be shown that $\alpha$ controls the false positive rate. $\alpha=5.0\%$ is a typical choice and is used throughout this thesis. Other fields use the $\sigma$ notation, for example $2\sigma$ correspond to about the $\alpha = 4.6\%$ significance level; this notation will not be used here.

Multiple hypothesis testing occurs when there are more than one hypotheses to test. For example $n$ pixels can be tested where the test statistics are $Z_1, Z_2, \dotsc, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\dotsc,n$. The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\dotsc,n$. Let the corresponding $p$-values be $p_1, p_2, \dotsc, p_n$.

@@

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c}
    &Negative&Positive&Total\\\hline
    Null & $U$ & $V$ & $n_0$\\
    Non-null & $T$ & $S$ & $n-n_0$\\\hline
    &$n-R$&$R$&$n$
  \end{tabular}
  \caption{Random variable definitions for the number of true/false positives/negatives made in multiple hypothesis testing}
  \label{table:inference_randomvariables}
\end{table}

The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the family-wise error rate (FWER) \citep{shaffer1995multiple} where
\begin{equation}
  \text{FWER} = \prob(V\geqslant1) \ .
  \label{eq:inference_fwer}
\end{equation}
This is done by adjusting the size of the test to be $\alpha/n$. By using the adjusted size, then $\text{FWER}=1-\left[(1-\alpha/n)^n\right]$. Using the approximation $(1-\alpha/n)^n\approx 1-\alpha$ then $\text{FWER}\approx \alpha$. This shows that the Bonferroni correction controls the family-wise error rate such that
\begin{equation}
  \text{FWER} \leqslant \alpha \ .
\end{equation}
However, in practice the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it gives too many false negatives. This is because the correction traded too many false positives for false negatives.

@@

The BH procedure adjust the size of the test between the Bonferroni correction and the uncorrected test. It adapts to the data and choose different sizes for different data. The procedure is as follows, the $p$-values are ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotsc \leqslant p_{(n)}$. Suppose a size $\alpha$ is provided beforehand. The size is adjusted to
\begin{equation}
  \alpha_{\text{BH}} = \frac{\alpha k}{n}
\end{equation}
where
\begin{equation}
  k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{n}\alpha
  \ .
\end{equation}
This test the statistics with $p$-values $p_{(1)},p_{(2)},\dotsc,p_{(k)}$ as positive. For the case where $p_{(1)}>\alpha/n$ then $k=1$ so that the Bonferroni correction is used when there are no positive results, this is only for illustration purposes. For example in Figure \ref{fig:inference_inferenceIntro_pvalue}, the $p$-values were plotted against their order so that the critical boundary was shown by a linear curve with gradient $\alpha/n$.

@@

\begin{table}
    \centering
    \begin{tabular}{c|c}
        Correction&Controls for\\\hline
        No correction&$\text{PCER}\leqslant\alpha$\\
        Bonferroni&$\text{FWER}\leqslant\alpha$\\
        BH&$\text{FDR}\leqslant\alpha$
    \end{tabular}
    \caption{Different types of corrections for multiple hypothesis testing are listed here, along with what they control for.}
    \label{table:inference_corrections}
\end{table}

Consider a small example where a $200\times200$ section of the $z$ image was investigated, as shown Figure \ref{fig:inference_inferenceSubsample1_histogram}. The distribution of the test statistics appeared Normal but not centred at zero. So by using the BH procedure to obtain a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$, almost half of the pixels were tested positive. It is questionable whether such a number of positive results is sensible, in particular in an area where defects were not expected.

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_zImage.eps}
      \caption{Test statistics}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_histogram.eps}
      \caption{Histogram of test in sub-image}
    \end{subfigure}
    }
    \caption{The resulting $z$ image is shown in a). A $200\times 200$ sub-image was taken shown by the dashed lines. A histogram of the test statistics in the sub-image is shown in b). The critical region was obtained by using the BH procedure at the 5\% FDR level.}
    \label{fig:inference_inferenceSubsample1_histogram}
\end{figure}

@@

In practice $\mu_0$ and $\sigma_0$ are unknown. The empirical null \citep{efron2004large} replaces the parameters of the null distribution with its estimate. Suppose $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ are the estimated null mean and null standard deviation respectively. The statistics are specified by $Z_i\sim\normal(\mu_i, \widehat{\sigma}_0^2)$ so that the following null hypotheses $H_{0,i}:\mu_i=\widehat{\mu}_0$ are tested against $H_{1,i}:\mu_i\neq\widehat{\mu}_0$ for $i=1,2,\dotsc,n$.

@@

The null standard deviation is estimated from the log density \citep{efron2004large}. For values of $z$ at and around the mode
\begin{equation}
  \ln p_{Z}(z) = 
  \ln\left[
    \dfrac{\pi_0}{\sqrt{2\pi}{\sigma}_0}
  \right]
  -\dfrac{1}{2}
  \left(
    \dfrac{z-{\mu}_0}{{\sigma}_0}
  \right)^2
  \ .
\end{equation}
Taking derivatives
\begin{align}
  \dfrac{\partial}{\partial z} \ln p_{Z}(z) &=
  -\left(
    \dfrac{
      z-{\mu}_0
    }
    {
      {\sigma}_0^2
    }
  \right)
  \nonumber\\
  &=
  -\dfrac{
    1
  }
  {
    {\sigma}_0^2
  }
\end{align}
which motivates the estimator \citep{efron2004large}
\begin{equation}
  \widehat{\sigma}_0 = \left[
    \left.
      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}(z)
    \right|_{z=\widehat{\mu}_0}
  \right]^{-1/2}
  \ .
  \label{eq:inference_nullStdEstimator}
\end{equation}
The evaluation of $z=\widehat{\mu}_0$ is used because at the mode, it was assumed that the null test statistics would dominate and non-null test statistics would not contribute much to the density estimate.

@@

The empirical null is used widely, including in neuroimaging \citep{schwartzman2008false, schwartzman2009empirical} and has been extended to include non-Normal null distributions \citep{schwartzman2008false, schwartzman2008empirical}. There exist various methods for the empicial null. \cite{schwartzman2008empirical} used Poisson regression on the histogram counts in regions where the null statistics dominate. The empirical characteristic function was used in \cite{jin2007estimating}.

@@

Returning back to the sub-image example in Figure \ref{fig:inference_inferenceSubsample1_histogram}. The histogram was smoothed using a kernel density estimate \citep{parzen1962on, friedman2001elements} as shown in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}. The kernel density estimate \citep{parzen1962on} is
\begin{equation}
  \widehat{p}_Z(z)=
  \frac{1}{nh}
  \sum_{i=1}^n\phi\left(
    \dfrac{z_i-z}{h}
  \right)
  \label{eq:inference_kernel_density_estimate}
\end{equation}
where $h$ is the bandwidth and $phi(x)$ is the standard Normal density. The bandwidth was chosen such that
\begin{equation}
  h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_z,\text{IQR}_z/1.34\right)
  \label{eq:inference_ourruleofthumb}
\end{equation}
where $s_z$ and $\text{IQR}_z$ are the sample standard deviation and sample interquartile range. This bandwidth is justified later on in this section.

\begin{figure}
  \centering
  \includegraphics[width=\subSize]{../figures/inference/inferenceSubsample1_densityEstimate.eps}
  \caption{The density of the test statistics was estimated using a kernel density estimate. The dot dash lines show the empirical null distribution multiplied by some constant, this is to illustrate that the two densities have the same curvature at the mode.}
  \label{fig:inference_inferenceSubsample1_densityEstimate}
\end{figure}

The null mean was estimated by numerically finding the mode of the density estimate. The null standard deviation was estimated using Equation \eqref{eq:inference_nullStdEstimator}. This results in the empirical null density to have the same curvature as the density estimate at the mode, this is illustrated in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}. In this particular example, it was found that $\widehat{\mu}_0=\input{../figures/inference/inferenceSubsample1_nullMean.txt}$ and $\widehat{\sigma}_0=\input{../figures/inference/inferenceSubsample1_nullStd.txt}$ to 2 decimal places.

@@

The test statistics were normalised to $T_1,T_2,\dotsc,T_n$ by using
\begin{equation}
  T_i = \dfrac{
    Z_i - \widehat{\mu}_0
  }
  {
    \widehat{\sigma}_0
  }
  \label{eq:inference_empiricalNullNormalise}
\end{equation}
for $i=1,2,\dotsc,n$. The normalised $p$-values were obtained by using
\begin{equation}
  p_i = 2(1-\Phi(|t_i|))
\end{equation}
and then were used in the BH procedure. The critical region was found to be $|t|\geqslant\inputNumber{../figures/inference/inferenceSubsample1_nullNormalisedCritical.txt}$. In terms of the original units, the critical region was $z \leqslant \inputNumber{../figures/inference/inferenceSubsample1_nullCritical1.txt}$ and $\inputNumber{../figures/inference/inferenceSubsample1_nullCritical2.txt}\leqslant z$, all to 2 decimal places. The critical region and the normalised $p$-values are shown in Figure \ref{fig:inference_inferenceSubsample1_nullResults}.

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_nullHistogram.eps}
        \caption{Histogram of $z$}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_nullPValues.eps}
        \caption{$p$-values}
    \end{subfigure}
    }
    \caption{Histogram of the test statistics from the sub-image in Figure \ref{fig:inference_inferenceSubsample1_histogram}. Also shown are the critical regions and $p$-values which were adjusted using the empirical null.}
    \label{fig:inference_inferenceSubsample1_nullResults}
\end{figure}

No positive results were found and the $p$-values were sensible as they resemble the uniformly distribution. This demonstrated that the empirical null adjusted the parameters of the null distribution to fit onto the majority of the data in order to make sensible inference.

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_zImage.eps}
        \caption{test statistics}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_subimagePositive.eps}
        \caption{$z$ from the sub-image}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_nullHistogram.eps}
        \caption{Histogram of $z$}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample2_nullPValues.eps}
        \caption{$p$ values}
    \end{subfigure}
    }
    \caption{A $200\times 200$ sub-image containing a defect is shown in a). The empirical null was used to test pixels, positive pixels are shown in red in b). The histogram of the test statistics are shown in c) along with the critical region. The normalised $p$-values are shown in d). The critical regions were adjusted using the empirical null and obtained using the BH procedure at the 5\% FDR level.}
    \label{fig:inference_inferenceSubsample2}
\end{figure}

Another example is shown in Figure \ref{fig:inference_inferenceSubsample2} where a $200\times 200$ sub-image containing a defect was used. It can be seen that the null distribution was not centred at zero, however the empirical null took it into account. The estimation of the empirical null parameters were robust as it depends on the density estimate at the mode only, it should not be affected by non-null test statistics.
